---
title: "Knowledge Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width = 4, fig.height = 4, fig.align = "center", dev='svg')
```

```{r}
library(openxlsx)
library(tidyverse)
library(ggthemes)
library(scales)
library(data.table)
library(haven)
library(pander)
library(lme4)
library(emmeans)
library(pander)
library(zoo)
library(pipeR)

panderOptions('table.split.table', Inf)

NICHE_colors <- c("#57068C","#6199AE","#FFC842","#314383","#6BAB8A","#F09C5D")
```

```{r}
giap <- read.xlsx("Complete Raw Data CMC.xlsx", detectDates = TRUE)

wrap_20 <- wrap_format(20)
wrap_30 <- wrap_format(30)
wrap_40 <- wrap_format(40)
```

```{r}
giap$LastInitial <- ifelse(is.na(giap$RecipientLastName), " ", toupper(substr(giap$RecipientLastName, 1, 1)))
giap$FirstInitial <- ifelse(is.na(giap$RecipientFirstName), " ", toupper(substr(giap$RecipientFirstName, 1, 1)))

giap <- mutate(giap, PID = Participant.ID,
                     UID = round(Unit.ID, 4),
                     HID = round(Hospital.ID, 4))
hosp <- read.xlsx("Master List of Variables.xlsx", sheet = "Invited Hospitals")
srost <- read.xlsx("Master List of Variables.xlsx", sheet = "Sampled Rosters")
arost <- read.xlsx("Master List of Variables.xlsx", sheet = "Participating - full rosters")
zips <- read.csv("free-zipcode-database-Primary.csv")
zips$ZIP5 <- str_pad(zips$Zipcode, 5, pad = "0")
hosp <- left_join(hosp, zips, by = c("Zip.code" = "ZIP5"))
hosp <- mutate(hosp, 
               Region = car::recode(State, "'MI'='MIDWEST';'OH'='MIDWEST';'IN'='MIDWEST';'MD'='SOUTH';'CA'='WEST';'PA'='NORTHEAST';'OR'='WEST';'MA'='NORTHEAST';'NY'='NORTHEAST';
                                    'CO'='WEST';'NJ'='NORTHEAST';'AZ'='WEST';'LA'='SOUTH';'RI'='NORTHEAST';'TN'='SOUTH';'FL'='SOUTH';'CT'='NORTHEAST';'TX'='SOUTH';'WI'='MIDWEST';'IL'='MIDWEST';'DC'='SOUTH'"),
               `Ownership(for.profit/not.for.profit/Government/Public)` = gsub("\n", "", `Ownership(for.profit/not.for.profit/Government/Public)`))
srost <- mutate(srost, Shift_Cat = car::recode(SHIFT_R, "0='Missing';1='Day (7am-3pm)';2='Evening (3pm-11pm)';3='Night (11pm-7am)';4='12HR Day(7am-7pm)';5='12HR Night (7pm-7am)';6='Part-time, variable'"),
                PID = round(Participant.ID, 4),
                UID = round(Unit.ID, 4),
                HID = round(Hospital.ID, 4),
                Survey = PID %in% na.omit(giap$PID),
                LastInitial = substr(Participant.Name, 1, 1),
                TENURE_IN_DAYS = ifelse(TENURE_IN_DAYS == 0, NA, TENURE_IN_DAYS))

```

```{r}
question_list <- read.xlsx("question_list.xlsx")
question_list <- na.locf(question_list)
question_list$Select <- c(1,2)
question_list <- question_list %>% filter(Select==2) %>% select(Code, Question)
```

```{r}
knowledge <- read.csv("knowledge_answers.csv")
knowledge$select <- c(1,2)
knowledge <- knowledge %>% filter(select == 1) %>% select(-select)

knowledge$Code<- gsub(pattern = "-", replacement = "_", 
                      gsub(pattern = " ", replacement = "", 
                           gsub(pattern = " –", replacement = "", 
                                substr(knowledge$Question, 11,16))))

knowledge$Answers <- strsplit(as.character(knowledge$Answer), "/")

knowledge <- knowledge %>% select(Code, Type, Answers)


trim <- function (x) gsub("^\\s+|\\s+$", "", x)

response_to_num <- function(x){
  response <- c()
  for(i in 1:length(x)){
    x[i] <- trim(x[i])
    response[i] <- case_when(x[i] == "Strongly Disagree" ~ 0,
                             x[i] == "Disagree" ~ 1,
                             x[i] == "Neither Agree nor Disagree" ~ 2,
                             x[i] == "Agree" ~ 3,
                             x[i] == "Strongly Agree" ~ 4)
  }

  return(response)
}

for(i in 1:nrow(knowledge)){
  knowledge[[3]][[i]] <- response_to_num(knowledge[[3]][[i]]) %>% list()
}

check_score <- function(row){
  temp <- row %>% 
    t() %>% 
    data.frame() %>% 
    mutate(Code = row.names(.)) %>% 
    left_join(knowledge, by = ("Code")) %>% 
    setNames(c("Response", "Code", "Type", "Answers")) %>% 
    rowwise() %>% 
    mutate(Points = ifelse(Response %in% (Answers %>% unlist), 1, 0))
  return(sum(temp$Points)/length(temp$Points))
}

```

In the report below, I have presented a histogram of the scores achieved by the nurses in the cohort with respect to the knowledge question. A 25% score indicates that they got 25% questions correct of all the questions, which range from 4 - 10 depending on the question set. 

I have also used all the questions from the original question set since the consistency does not matter in this case, since the answers are objective. 

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q5_7, Q5_8, Q5_14, Q5_21, Q5_24, Q5_25, Q5_26, Q5_33, Q20_31, Q20_32) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID)

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


fall <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Falls")

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Falls") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question"))
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q20_40, Q20_42, Q20_48, Q5_1) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID)

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


restraints <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Restraints") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Restraints") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q20_43, Q20_44, Q20_47, Q5_6, Q20_37, Q20_38, Q20_46) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID) 

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


skin <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Skin")

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Skin") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q5_3, Q5_4, Q20_7, Q20_8, Q20_9, Q20_12, Q20_13, Q20_14, Q5_5) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID) 

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}
score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


incontinence <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Incontinence") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Incontinence") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q5_9, Q5_23, Q20_17, Q20_18, Q20_15) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID) 

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


pain <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Pain") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Pain") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q20_20, Q20_58, Q20_19, Q20_51, Q20_55) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID) 

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


delirium <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Delirium") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Delirium") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q20_26, Q20_29, Q5_20, Q20_22) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID) 

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


dementia <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Dementia") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Dementia") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r}
set <- giap %>%
  filter(!is.na(Hospital.ID)) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, 
         Q5_11, Q5_19, Q5_13, Q20_33, Q20_51) %>%
  gather(Item, Response, -Hospital.ID, -Unit.ID, -Participant.ID) %>% 
  filter(!is.na(Response)) %>%
  mutate(Response_N = as.numeric(substr(Response, 1, 1)) - 1) %>%
  select(Hospital.ID, Unit.ID, Participant.ID, Item, Response_N) %>%
  spread(Item, Response_N) %>%
  select(-Hospital.ID, -Unit.ID, -Participant.ID)

score <- c()

for(i in 1:nrow(set)){
  score[i] <- check_score(set[i,])
}

score <- score %>% data.frame() %>% setNames("Score")
score <- score %>%
  mutate(Grade = case_when(Score < .50 ~ "Poor",
                           Score >= .50 & Score < .70 ~ "Fair",
                           Score >= .70 & Score < .90 ~ "Good",
                           Score >= .90 ~ "Very Good"),
         Grade = ordered(Grade, levels = c("Poor","Fair","Good","Very Good")))


nutrition <- score %>%
  count(Grade) %>%
  mutate(Percent = round(n / sum(n) * 100),
         Question = "Nutrition") 

mean_list <- score$Score %>% 
  mean %>% 
  cbind("Nutrition") %>% 
  data.frame() %>% 
  setNames(c("Mean", "Question")) %>%  
  rbind(mean_list)
```

```{r fig.height = 7, fig.width = 10}
cols <- c("Poor" = "#AE6180", 
          "Fair" = "#A3A9AC", 
          "Good" = "#FFC842", 
          "Very Good" = "#6BAB8A")

question_levels <- c("Delirium", "Dementia", "Falls", "Incontinence", "Nutrition", "Pain", "Restraints", "Skin")

mean_list$Mean <- as.numeric(as.character(mean_list$Mean))

list(fall, restraints, skin, incontinence, pain, 
     delirium, dementia, nutrition, mean_list) %>% 
  reduce(full_join) %>%
  mutate(Grade = ordered(Grade, 
                         levels = c("Very Good", "Good", "Fair", "Poor")),
         Question = ordered(Question, levels = rev(question_levels))) %>%
  ggplot(aes(x = Question, y = Percent/100, fill = Grade)) +
  geom_bar(position = "fill", stat = "identity", width = 0.06 * 11, color = "white") +
  geom_point(aes(x=Question, y=Mean), shape = 8, size = 2, show.legend = FALSE, stroke = 0.5) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = cols) +
  labs(y = "", x = "", fill = "") +
  theme_minimal() +
  theme(legend.position = "right", 
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10)) +
  coord_flip()
```

